Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{EIP-150 revision (\YellowPaperVersionNumber{})}}

### 2018-01-20 Paper.tex
Update \expdiffsymb explanation

The canonical gas limit $H_l$ of a block of header $H$ must fulfil the relation:
\begin{eqnarray}
& & H_l < {P(H)_H}_l + \left\lfloor\frac{{P(H)_H}_l}{1024}\right\rfloor \quad \wedge \\
& & H_l > {P(H)_H}_l - \left\lfloor\frac{{P(H)_H}_l}{1024}\right\rfloor \quad \wedge \\
& & H_l \geqslant 5000
\end{eqnarray}

>>>>

Note that $\mindifficulty$ is the difficulty of the genesis block. The \textit{\href{https://github.com/ethereum/EIPs/blob/master/EIPS/eip-606.md}{Homestead} difficulty parameter, $\homesteadmod$, is used to affect a dynamic homeostasis of time between blocks, as the time between blocks varies, as discussed below. $\expdiffsymb$ results in the difficulty increasing every 10000 blocks, which puts upward pressure on the time between blocks, causing it to slowly accelerate, and putting time pressure on transitioning to proof-of-stake.

The canonical gas limit $H_l$ of a block of header $H$ must fulfil the relation:
\begin{eqnarray}
& & H_l < {P(H)_H}_l + \left\lfloor\frac{{P(H)_H}_l}{1024}\right\rfloor \quad \wedge \\
& & H_l > {P(H)_H}_l - \left\lfloor\frac{{P(H)_H}_l}{1024}\right\rfloor \quad \wedge \\
& & H_l \geqslant 125000
\end{eqnarray}
